\documentclass[12pt,a4paper]{article}


\usepackage[utf8]{inputenc}
\usepackage[margin=0.5 in]{geometry}
\usepackage[hidelinks]{hyperref}
\urlstyle{same}
% Setting Fonts
% \usepackage{mathspec}					% This loades the fontspec package as well
% %\usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}
% %\usepackage[sf,big,bf]{titlesec}
% %\usepackage{titling}

\usepackage{tikz}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
% %\setromanfont{Adobe Garamond Pro}
% \setromanfont{Adobe Caslon Pro}
% \setsansfont{Myriad Pro}

%\setmathfont{Adobe Garamond Pro}
% \setmathfont{Adobe Caslon Pro}

% Left align abstract title
\renewenvironment{abstract}
  {\small\quotation
  {\itshape\noindent{\normalsize\abstractname}\par\nobreak\smallskip}}
  {\endquotation}

\pagenumbering{gobble}
\begin{document}
	
	\begin{center}

	\textsf{{\LARGE\textbf{Jonathan Lee Norris}}}		
	\smallskip	
	
	\textsf{{\Large \textbf{Curriculum Vitae}}} 
	\smallskip
	
	\textsf{jonathan.norris@strath.ac.uk}

	\textsf{\url{https://www.strath.ac.uk/staff/norrisjonathandr/}}	
	\end{center}	
	% \hrule height 1pt

	\bigskip

	\noindent {\textbf{\textsf{\large Current Post}}} \vspace{0.1cm} \hrule \vspace{0.2cm}

		\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); \textit{Lecturer}. The University of Strathclyde Department of Economics. 

	\bigskip	

	\noindent \textbf{\textsf{{\large Education}}}   \vspace{0.1cm} \hrule \vspace{0.2cm}		
		%\smallskip
			\begin{itemize}
			\item[$\circ$] 2018 PhD in Economics, \textit{UNC Greensboro}	
			\item[$\circ$] 2013 Master of Arts in Applied Economics, \textit{UNC Greensboro}  
			\item[$\circ$] 2012 Bachelor of Science in Economics, \textit{UNC Greensboro}	
			\end{itemize}

	\bigskip
	
	\noindent \textbf{\textsf{{\large Fields of Interest}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}	
		%\smallskip
		
			\noindent Applied Economics, Economics of Education, Labor Economics, Inequality	
		
	\bigskip

	\noindent \textbf{\textsf{{\large Publications}}} \vspace{0.1cm} \hrule \vspace{0.2cm}

		\begin{itemize}
		\item[$\circ$] Peers, Parents, and Attitudes about School. \textit{Journal of Human Capital} 14, no. 2 (2020): 290-342
		\item[$\circ$] The Skill Development of Children of Immigrants (\textit{with Marie Hull}). \textit{Economics of Education Review} 78 (2020): 102036
		\item[$\circ$] Identity Economics: Social Influence and Skill Development. \textit{Journal of Economic Surveys} 33, no. 5 (2019): 1389-1408
		\end{itemize}
		
	\bigskip 
	
	\noindent \textbf{\textsf{{\large Working Papers}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}  

		\begin{itemize}
		\item[$\circ$] The Long-Run Effects of Peers on Mental Health (\textit{with Lukas Kiessling}) [conditionally accepted at the Economic Journal]
		\item[$\circ$] Troubled in School? Does Maternal Involvement Matter for Adolescents? (\textit{with Martijn van Hasselt})
		\item[$\circ$] Peer Gender and School: Evidence from Ethiopia (\textit{with Daniel Borbely \& Agnese Romiti})
		\end{itemize}
		
	\bigskip

	\noindent \textbf{\textsf{{\large Research in-Progress}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}  

		\begin{itemize}
		\item[$\circ$] Reference Dependence and Peer Effects (\textit{Marco Fongoni, Agnese Romiti, \& Zhan Shi})
		\item[$\circ$] Marijuana Legalization and Mental Health (\textit{with Daniel Borbely, Otto Lenhart, \& Agnese Romiti})
		\item[$\circ$] Asymmetry in Intensity and Persistence of Reciprocity in Labour Markets (\textit{with Alex Dickson \& Marco Fongoni}) 	
		\end{itemize}

	\newpage
	\noindent \textbf{\textsf{{\large Knowledge Exchange Publications}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}	

		\begin{itemize}
		\item[$\circ$] The economics of parenting: children and inequality in a time of shutdown (\textit{with Emma Congreve}). Fraser of Allander Commentary 44, no. 2 (2020).
		\item[$\circ$] How is coronavirus affecting the mental health of adolescents? \textit{Economics Observatory}. Published online 31 August 2020. \href{https://www.economicsobservatory.com/how-coronavirus-affecting-mental-health-adolescents}. 
		\item[$\circ$] Update: How is coronavirus affecting the mental health of adolescents? \textit{Economics Observatory}. Published online 8 September 2021. \href{https://www.economicsobservatory.com/update-how-is-coronavirus-affecting-the-mental-health-of-adolescents}. 
		\end{itemize}

		\bigskip

	\noindent \textbf{\textsf{{\large Seminar and Conference Presentations}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}		
		%\smallskip

		\begin{itemize}
		\item[$\circ$] 2022: Scottish Economic Society Annual Conference	
		\item[$\circ$] 2021: Annual Conference of the European Society for Population Economics (Virtual)
		\item[$\circ$] 2020: 2nd Workshop on Health and Inequality at Copenhagen Business School (Virtual)
		\item[$\circ$] 2019: Seminar at UCD Geary Institute
		\item[$\circ$] 2019: 34th National Conference of Labour Economics
		\item[$\circ$] The Society of the Economics of the Household 3rd Annual Meetings
		\item[$\circ$] 2016: Southern Economics Association 86th Annual Meetings 
		\end{itemize}

	\bigskip

	\noindent \textbf{\textsf{{\large Awards}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}

		\begin{itemize}
			\item[$\circ$] 2022: University of Strathclyde Student Excellence Award (PhD student funding)
			\item[$\circ$] 2020: University of Strathclyde Research Excellence Scholarship (PhD student funding)
			\item[$\circ$] 2022: Teaching excellence award shortlist for best in faculty
		\end{itemize}

	\bigskip

	\noindent \textbf{\textsf{{\large PhD Supervision}}}  \vspace{0.1cm} \hrule \vspace{0.2cm}

		\begin{itemize}
			\item[$\circ$] 2021-present: Zhan Shi (1st supervisor)
			\item[$\circ$] 2021-present: Cesarine Boinet (2nd supervisor)
			\item[$\circ$] 2022 (starting): Tham Ta (1st supervisor)
		\end{itemize}

	\bigskip	

	\noindent \textbf{\textsf{{\large Teaching Experience}}}	 \vspace{0.1cm} \hrule \vspace{0.2cm}	

		\begin{itemize}
		\item[$\circ$] 2020-present: Health Economics, MSc. (U. Strathclyde)
		\item[$\circ$] 2019-present: Inequality Economics, MSc. (U. Strathclyde)
		\item[$\circ$] 2019-present: Applied Econometrics, 4th Year Honours (U. Strathclyde)
		\item[$\circ$] 2019-present: Industrial Economics, 4th Year Honours (U. Strathclyde)
		\item[$\circ$] BA and MSc Dissertation Advisor (U. Strathclyde)
		\item[$\circ$] 2017 Instructor for Principles of Microeconomics  (UNC Greensboro)
		\item[$\circ$] 2015-2017 Instructor for Business Statistics I  (UNC Greensboro)
		\end{itemize}

	\bigskip
	
	\noindent \textbf{\textsf{{\large Professional Service}}}	 \vspace{0.1cm} \hrule \vspace{0.2cm}	

		\begin{itemize}
		\item[$\circ$] Refereeing Activity: \textit{Economic Journal}, \textit{Labour Economics}, \textit{Behavioural Public Policy}, \textit{Economics of Education Review}
		\end{itemize}

	% \newpage
	% \noindent {\large\textbf{Skills and Non-Academic Experience}} \vspace{0.1cm} \hrule \vspace{0.2cm}
	% 	%\smallskip
		
	% 		\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); Programming: Stata, Matlab, SAS, \LaTeX
	% 		\medskip
	
	% 		\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); Service Learning: 2015-2016 AmeriCorps Access Project Volunteer Youth Coordinator, \textit{The Center for New North Carolinians}
	% 		\medskip
	
	% 		\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); Military Service:
	% 		\smallskip
				
	% 			\indent 2004-2008 Active Duty US Army \\ 
	% 			% \indent \textit{Deployment}: Iraq (June 2006 - September 2007)	\\
	% 			\indent 2010-2016 US Navy Reserves	    \\
	
	% \bigskip

	% \noindent {\large \textbf{References}} \vspace{0.1cm} \hrule \vspace{0.2cm}
	% %\smallskip
		
	% 	\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); Dr. Jeremy Bray; Email: \href{mailto:jwbray@uncg.edu}{jwbray@uncg.edu}				
	% 	\medskip
		
	% 	\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); Dr. Martijn van Hasselt; Email: \href{mailto:mnvanhas@uncg.edu}{mnvanhas@uncg.edu}
	% 	\medskip
		         
	% 	\noindent \tikz\draw[black,fill=white] (0,0) circle (.5ex); Dr. Dora Gicheva; Email: \href{mailto:d\_gichev@uncg.edu}{d\_gichev@uncg.edu}




\end{document}